Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Henry context

Diego is a 5 years hold child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

@@

\subsubsection{Context, Study Design}

>>>>

Diego is a 6 years hold child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

@@

\subsubsection{Context, Study Design}
Henry is a five and half years hold child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Henry
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Henry is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two chalenging issues
(visuo-constructive deficits and inattention) in order to keep Henry focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a complex cenario like the one for Diego was
no longer relevent with Henry. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\
